A* with Perfect Potentials

### 2020-04-09 paper/ch_potentials.tex
foo

\section{A*}

@@

\section{CH}

@@

\section{Phast}

@@

TODO: Everything below is old.

\section{Skipping Degree Two Chains}

\begin{algorithm2e}
\KwData{$D[x]$ tentative distance from $s$ to $x$, initially $+\infty$}
\KwData{$Q$ minimum priority queue of nodes}
$D[a_s]\leftarrow 0$\;
Add $a_s$ to $Q$ with weight $\pi(a_s)$\;
\While{not $Q$ empty}{
  $x\leftarrow$ pop node from $Q$\;
  \If{$x = a_t$}{finished\;}
  \For{all edges $(x,y)$ in the core graph $G_C$}{
    $\alpha\leftarrow x$;
    $\beta\leftarrow y$;
    $w\leftarrow w_q(\alpha,\beta)$\;
    \While{undirected degree of $\beta$ is 2 and $z\neq a_t$}{
      $\gamma\leftarrow$ neighbor of $\beta$ in $G_C$ different from $\alpha$\;
      $w\leftarrow w+w_q(\beta,\gamma)$;
      $\alpha\leftarrow \beta$;
      $\beta\leftarrow \gamma$\;
    }
    \If{$D[x]+w < D[\beta]$}{
        $D[\beta]\leftarrow D[x]+w$\;
    	Add $\beta$ to Q with weight $D[\beta]+\pi(\beta)$\;
    }
  }
}
\caption{A* star search in the core skipping degree two nodes}
\label{algo:skip-a-star}
\end{algorithm2e}

The core graph $G_C$ contains a lot of degree two nodes \cite{TOPOCORE}.
At such nodes no directional decision is made.
It is therefore unecessary to evaluate the potentials at these nodes.

We exploit this intuition by modifying the A* search.
When exploring the neighbors $y$ of node $x$, we follow chains of degree two nodes until a node $\beta$ with degree at least three is found.
Instead of $y$, we add $\beta$ to the queue.
No queue operations nor potential evaluations are required for the intermediate degree two nodes.

\section{Skipping Trees}

TODO @ Tim, bringt das wirklich was?

>>>>

\section{Goal-Directed Search using A*}

@@

\section{Contraction Hierarchy (CH)}

@@

\section{Potentials using PHAST}

@@
